---
title: "000-HUDECA-HYPO — FIGURES"
author: "Yvon Mbouamboua <yvon.mbouamboua@inserm.fr>"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
date: '`r format(Sys.Date())`'
---

## Goal
Final figures

## Setup
```{r setup, message=FALSE, warning=FALSE}

knitr::opts_chunk$set(message = FALSE, warning = FALSE)
root <- '/Users/yvon.mbouamboua/projects/singlecell/10x-hudeca-hypo'
outdir <- file.path(root, 'output', 'figures')
if (!dir.exists(outdir)) dir.create(outdir, recursive = TRUE, showWarnings = FALSE)
shared_root <- normalizePath('~/projects/cellverse/R', winslash = '/', mustWork = FALSE)
load_r <- function(d) {
  if (dir.exists(d)) {
    fs <- sort(list.files(d, '\\.R$', full.names = TRUE))
    invisible(lapply(fs, sys.source, envir = .GlobalEnv))
  }
}
load_r(file.path(shared_root, 'helper'))
import_dir <- file.path(shared_root, 'import')
pkg <- file.path(import_dir, 'packages.R')
if (file.exists(pkg)) sys.source(pkg, envir = .GlobalEnv)
load_r(import_dir)

```

All functions used in this analysis can be found here: https://github.com/ymbouamboua/HuDeCa/blob/main/R/000-functions.R.

# Load data

```{r}

obj = readRDS(file.path(root, "output/analysis/data/fh.rds"))
pal <- readRDS(file.path(root, "analysis/hudeca_hypo_colors.rds"))

```


# QC

```{r}

raw <- readRDS("~/projects/singlecell/10x-hudeca-hypo/output/preprocessing/data/raw.rds")
raw = get_subset(raw, group.by = "BulkSample", idents = "unassigned", invert=T)
unique(raw$BulkSample)
raw$percent_mito <- PercentageFeatureSet(raw, pattern = "^MT-")

raw@meta.data <- raw@meta.data %>%
  dplyr::mutate(
    sample = case_when(
      BulkSample == "S1-PCW7" ~ "S1",
      BulkSample == "S2-PCW8" ~ "S2",
      BulkSample == "S5-PCW10" ~ "S3",
      BulkSample == "S4-PCW10.5" ~ "S4",
      BulkSample == "S6-PCW12" ~ "S5",
      BulkSample == "S7-PCW12" ~ "S6",
      BulkSample == "S8-PCW12" ~ "S7"
    ),
    status = case_when(
      BulkSample == "S1-PCW7" ~ "S1-PCW7-LD",
      BulkSample == "S2-PCW8" ~ "S2-PCW8-LD",
      BulkSample == "S5-PCW10" ~ "S3-PCW10-LD",
      BulkSample == "S4-PCW10.5" ~ "S4-PCW10.5-OD",
      BulkSample == "S6-PCW12" ~ "S5-PCW12-OD",
      BulkSample == "S7-PCW12" ~ "S6-PCW12-LD",
      BulkSample == "S8-PCW12" ~ "S7-PCW12-LD"
    ),
    stage = case_when(
      BulkSample %in% c("S1-PCW7") ~ "PCW7",
      BulkSample %in% c("S2-PCW8") ~ "PCW8",
      BulkSample %in% c("S5-PCW10","S4-PCW10.5") ~ "PCW10",
      BulkSample %in% c("S6-PCW12","S7-PCW12","S8-PCW12") ~ "PCW12"
    ),
    bmi = case_when(
      BulkSample == "S1-PCW7" ~ "LD7",
      BulkSample == "S2-PCW8" ~ "LD8",
      BulkSample == "S5-PCW10" ~ "LD10",
      BulkSample == "S4-PCW10.5" ~ "OD10.5",
      BulkSample == "S6-PCW12" ~ "OD12",
      BulkSample %in% c("S7-PCW12","S8-PCW12") ~ "LD12"
    ),
    group = case_when(
      BulkSample %in% c("S1-PCW7","S2-PCW8") ~ "LD7-8",
      BulkSample %in% c("S5-PCW10","S7-PCW12","S8-PCW12") ~ "LD10-12",
      BulkSample %in% c("S4-PCW10.5","S6-PCW12") ~ "OD10-12"
    ),
    cond = case_when(
      BulkSample %in% c("S1-PCW7","S2-PCW8","S5-PCW10","S7-PCW12","S8-PCW12") ~ "LD",
      BulkSample %in% c("S4-PCW10.5","S6-PCW12") ~ "OD"
    ),
    sex = case_when(
      BulkSample %in% c("S1-PCW7","S4-PCW10.5","S6-PCW12","S8-PCW12") ~ "M",
      BulkSample %in% c("S2-PCW8","S5-PCW10","S7-PCW12") ~ "F"
    )
  ) %>%
  dplyr::mutate(
    sample = factor(sample, levels = c("S1","S2","S3","S4","S5","S6","S7")),
    status = factor(status, levels = c("S1-PCW7-LD","S2-PCW8-LD","S3-PCW10-LD","S4-PCW10.5-OD","S5-PCW12-OD","S6-PCW12-LD","S7-PCW12-LD")),
    stage  = factor(stage, levels = c("PCW7","PCW8","PCW10","PCW12")),
    bmi    = factor(bmi, levels = c("LD7","LD8","LD10","OD10.5","OD12","LD12")),
    group  = factor(group, levels = c("LD7-8","LD10-12","OD10-12")),
    cond   = factor(cond, levels = c("LD","OD")),
    sex    = factor(sex, levels = c("M","F"))
  )


```


```{r fig.width=4, fig.height=6}

p = cellvio(raw, group.by = "status", features = c("nCount_RNA", "nFeature_RNA", "percent_mito"),
          cols = pal$status, stack = T, pt.size = 0.1, txtsize = 12, title = "Raw data", assay = "RNA", slot = "counts")
p
savefig(fig = p, filename = file.path(outdir, "plots/cellvio_qc_raw"),  width = 4, height = 6, format = "png")

p=cellvio(obj, group.by = "status", features = c("nCount_RNA", "nFeature_RNA", "percent_mito"),
          cols = pal$status, stack = T, pt.size = 0.1, txtsize = 12, title = "Filtered data", assay = "RNA", slot = "data")
p
savefig(fig = p, filename = file.path(outdir, "plots/cellvio_qc_filt"),  width = 4, height = 6, format = "png")

```


```{r}

QC_summary <- read_csv("~/projects/singlecell/10x-hudeca-hypo/output/preprocessing/data/QC_summary.csv")

QC_summary <- QC_summary %>%
  dplyr::mutate(
    status = case_when(
      Sample == "S1-PCW7" ~ "S1-PCW7-LD",
      Sample == "S2-PCW8" ~ "S2-PCW8-LD",
      Sample == "S5-PCW10" ~ "S3-PCW10-LD",
      Sample == "S4-PCW10.5" ~ "S4-PCW10.5-OD",
      Sample == "S6-PCW12" ~ "S5-PCW12-OD",
      Sample == "S7-PCW12" ~ "S6-PCW12-LD",
      Sample == "S8-PCW12" ~ "S7-PCW12-LD"
    )
  )
    
    
qc_long <- QC_summary |>
  pivot_longer(
    c(Pre_Cells, Post_Cells),
    names_to = "Stage",
    values_to = "Cells"
  ) |>
  dplyr::mutate(
    Stage = factor(Stage, levels = c("Pre_Cells", "Post_Cells"))
  )


p = ggplot(qc_long, aes(x = status, y = Cells, fill = Stage)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(
    values = c(
      "Pre_Cells"  = "gray20",
      "Post_Cells" = "#4E79A7"
    )
  ) +
  labs(
    title = "Cell counts before and after QC",
    y = "Number of cells",
    x = ""
  ) +
  plot_theme(x.ang = 45) 

p

savefig(fig = p, filename = file.path(outdir, "plots/barplot_qc"),  width = 4, height = 3, format = "png")
savetbl(p@data, file = file.path(outdir, "data/barplot_qc"), format = "xlsx")

ggplot(QC_summary, aes(x = Sample, y = Removed_Pct)) +
  geom_col(fill = "#E15759", width = 0.7) +
  geom_text(aes(label = paste0(Removed_Pct, "%")),
            vjust = -0.4, size = 3.5) +
  labs(title = "Percentage of cells removed by QC",
       y = "Removed cells (%)",
       x = "") +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



```


## Markers

```{r fig.width=6, fig.height=10}

sub = get_subset(sobj = obj, group.by = "ann1", idents = "Neuron")
cellmap(sub, group.by = "ann3")
sub <- genefilter(sub)
markers <- cellmarker(sub,  group.by = "ann3", only.pos = T, logfc.threshold = 0.25, min.pct = 0.25)
write.table(markers, file.path(outdir, "data/neuron_markers.tsv"), sep = "\t", row.names = F, quote = F)
obj@misc$neuron_markers <- markers
markers <- read.delim(file.path(outdir, "data/neuron_markers.tsv"))
top <- markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC)
p = celldot(sub, features = rev(top$gene), flip = T, group.by = "ann3", txtsize = 10, x.ang = 45, title = "Neurons", th.cols = "RdYlBu", rev.th.cols = T) 
p
savefig(p, filename = file.path(outdir, "plots/neuron_markers"),  width = 6, height = 10, format = "png")

```

## RGC

```{r fig.width=4.5, fig.height=7}

sub = get_subset(sobj = obj, group.by = "ann1", idents = c("RGC","Ependymal","Oligodendrocyte","Astrocyte","IPC","Tanycyte","TSC","NCC"))
cellmap(sub, group.by = "ann3")
sub <- genefilter(sub)
markers <- cellmarker(sub,  group.by = "ann3", only.pos = T, logfc.threshold = 0.25, min.pct = 0.25)
write.table(markers, file.path(outdir, "data/rgc_markers.tsv"), sep = "\t", row.names = F, quote = F)
obj@misc$rgc_markers <- markers
markers <- read.delim(file.path(outdir, "data/rgc_markers.tsv"))
top <- markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC)
p = celldot(sub, features = rev(top$gene), flip = T, group.by = "ann3", txtsize = 10, x.ang = 45, title = "RGCs", th.cols = "RdYlBu", rev.th.cols = T) 
p
savefig(p, filename = file.path(outdir, "plots/rgc_markers"),  width = 4.5, height = 7, format = "png")

```


## Vascular+Immune+Pitutary+Myogenic

```{r fig.width=4, fig.height=5}

sub = get_subset(sobj = obj, group.by = "ann1", idents = c("Mesenchyme","Vascular","Pituitary","Myogenic","Immune"))
cellmap(sub, group.by = "ann3")
sub <- genefilter(sub)
markers <- cellmarker(sub,  group.by = "ann3", only.pos = T, logfc.threshold = 0.25, min.pct = 0.25)
write.table(markers, file.path(outdir, "data/mes_vasc_pit_myog_imm_markers.tsv"), sep = "\t", row.names = F, quote = F)
obj@misc$mes_vasc_pit_myog_imm_markers <- markers
markers <- read.delim(file.path(outdir, "data/mes_vasc_pit_myog_imm_markers.tsv"))
top <- markers %>% group_by(cluster) %>% top_n(n = 3, wt = avg_log2FC)
p = celldot(sub, features = rev(top$gene), flip = T, group.by = "ann3", txtsize = 10, x.ang = 45, title = "Mes-Vasc-Pit-Myog-Imm", th.cols = "RdYlBu", rev.th.cols = T) 
p
savefig(p, filename = file.path(outdir, "plots/mes_vasc_pit_myog_imm_markers"),  width = 4, height = 5, format = "png")

```



# umap annlevels

```{r }

p <- cellmap(object = obj, group.by = c("ann1"), label = T, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$ann1,leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_ann1"),  width = 7, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("ann2"), label = T, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$ann2,leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_ann2"),  width = 7, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("ann3"), label = T, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$ann3,leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_ann3"),  width = 8, height = 5, format = "png")


p <- cellmap(object = obj, group.by = c("group"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$group,leg.size = 8, leg.pos = "bottom", leg.ncol = 3)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_group"),  width = 5, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("cond"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$cond,leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_cond"),  width = 7, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("sex"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$sex,leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_sex"),  width = 7, height = 5, format = "png")


p <- cellmap(object = obj, group.by = c("sample"), label = F, legend = T, txtsize = 10,plot.ttl = "N = 57,562 cells",
              figplot = T, label.size = 3, cols = pal$sample, label.face = "bold",leg.size = 8)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_sample"),  width = 7, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("status"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$status, label.face = "bold",leg.size = 8,leg.pos = "bottom", leg.ncol = 4)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_status"),  width = 5, height = 5, format = "png")


p <- cellmap(object = obj, group.by = c("stage"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$stage, label.face = "bold",leg.size = 8,leg.pos = "bottom", leg.ncol = 2)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_stage"),  width = 5, height = 5, format = "png")

p <- cellmap(object = obj, group.by = c("bmi"), label = F, legend = T, txtsize = 10,
              figplot = T, label.size = 3, cols = pal$bmi, label.face = "bold", leg.pos = "bottom", leg.ncol = 3)
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_bmi"),  width = 5, height = 5, format = "png")

```


```{r fig.width=12, fig.height=5, warning=F, message=F}

p <- cellmap(object = obj, group.by = "status", split.by = "status", label= F, figplot = F, plot.ttl = NULL,
              legend = F, cols = pal$status, txtsize = 20, pt.size = 0.5, ncol = 4, axes = F, style = "dirty") 
p
savefig(fig = p, filename = file.path(outdir, "plots/umap_split_status"),  width = 12, height = 5, format = "png")

```



# Cell correlation

```{r fig.width=8, fig.height=7}

cellcorr(obj, group.by = "ann3", assay = "RNA", fontsize = 10,  column_names_rot = 90, 
         pdf_width = 8, pdf_height = 7, fig_name = "cell_correlation", save = T, dir.results = file.path(outdir, "plots/"))

```





```{r fig.width=10, fig.height=8}
cellfeat(obj, features = c("HESX1","LHX3","LH4X","OTX2","GH1","LHB","PROP1","SF1", "FSHB","TSH"))
cellvio(obj, c("GH1","POMC","HESX1","LHX3", "POU1F1","TBX19"), group.by = "ann3", pt.size = 0.1, stack = T)
```

# Sample info

```{r}
cellstats(object = obj, ident = "status", group.by = c("sex"), rm.pct = T)

p = cellstats(object = obj, ident = "ann3", group.by = c("status", "sex"), rm.pct = T)
savetbl(df = p, file = file.path(outdir, "data/cellstats"), format = "xlsx")

```






```{r fig.width=12, fig.height=14}

p <- sankey_plot(obj, 
                   selected_vars = c("ann1", "ann2","ann3"),
                   show_percentages = TRUE, 
                   custom_colors = pal,
                   show_counts = FALSE, 
                   show_labels = TRUE,
                   flow.alpha = 0.5,
                   label.justify = "right", 
                   label.nudge = 0.5, text.size = 14,
                   prevent_overlap = TRUE)

print(p)
savefig(fig = p, filename = file.path(outdir, "plots/sankey"),  width = 12, height = 14, format = "png")

```





# Cell proportions

```{r fig.width=4, fig.height=6}

p = cellprop(data = obj, x = "ann3", y = "sample", stack = T, prop = T, flip = T, x.ttl = "", x.ang = 0, cols = pal$sample, contour = F)
p
savefig(p, filename = file.path(outdir, "plots/cellprop_sample_ann3"),  width = 4, height = 6, format = "png")

p = cellprop(data = obj, x = "ann3", y = "bmi", stack = T, prop = T, flip = T, x.ttl = "", x.ang = 0, cols = pal$bmi, contour = F)
p
savefig(p, filename = file.path(outdir, "plots/cellprop_bmi_ann3"),  width = 4, height = 6, format = "png")


p = cellprop(data = obj, x = "ann3", y = "group", stack = T, prop = T, flip = T, x.ttl = "", x.ang = 0, cols = pal$group, contour = F)
p
savefig(p, filename = file.path(outdir, "plots/cellprop_group_ann3"),  width = 4, height = 6, format = "png")

p = cellprop(data = obj, x = "ann3", y = "stage", stack = T, prop = T, flip = T, x.ttl = "", x.ang = 0, cols = pal$stage, contour = F)
p
savefig(p, filename = file.path(outdir, "plots/cellprop_stage_ann3"),  width = 4, height = 6, format = "png")

```



```{r fig.width=3, fig.height=3}

sub <- get_subset(obj, group.by = "group", idents = c("N10-12","O10-12"))
sub <- get_subset(sub, group.by = "ann3", idents = c("TBX3","POMC","AGRP","KISS1"))

p = cellprop(data = sub, x = "ann3", y = "group", stack = T, prop = T, x.title = "",x.ang = 45, txtsize = 12,  show.contour = T,x.reverse = T, colors = pal$group)
p
savefig(p, filename = file.path(outdir, "plots/cellprop_tbx3_pomc_agrp_kiss1"),  width = 3, height = 3, format = "png")

```

# scPermutation testing



```{r fig.width=5, fig.height=8}

Idents(obj) <- "ann3"
prop_test <- scProportionTest::sc_utils(obj)
prop_test <- scProportionTest::permutation_test(prop_test, cluster_identity = "ann3", sample_1 = "LD10-12", sample_2 = "OD10-12", sample_identity = "group", n_permutations = 10000)

savetbl(prop_test@results, file = file.path(outdir, "data/permut_test"), format = "xlsx")

p <- cellpermut(
  df = prop_test@results,
  mode = "log2FD",
  cluster.col = "clusters",
  group.cols = c("LD10-12","OD10-12"),
  plot.ttl = "scPermut test OD10-12 vs LD10-12",
  style = "bw", leg.pos = "bottom"
)

p
savefig(p, filename = file.path(outdir, "plots/permut_test"),  width = 5, height = 8)


# p <- cellpermut(
#   df = prop_test@results,
#   mode = "prop",
#   cluster.col = "clusters",
#   group.cols = c("LD10.12","OD10.12"),
#   plot.ttl = "scPermut test OD10-12 vs LD10-12",
#   style = "bw",
#   leg.pos = "bottom"
# )
# p

```

# umap of candidate markers

```{r fig.width=6, fig.height=7}

p <- cellfeat(obj, features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"), 
              axes = F, merge.leg = T, theme.cols = "inferno", order = T, ncol = 3)
p
savefig(p, filename = file.path(outdir, "plots/candidate_genes"),  width = 6, height = 7, format = "png")

```


# celldot candidate genes

```{r fig.width=5, fig.height=8}

p <- celldot(obj, features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"),
             group.by = "ann3", x.ang = 45, flip = F)
p
savefig(p, filename = file.path(outdir, "plots/fig4b"),  width = 5, height = 8)

```



# POMC + TBX3 highlight

```{r fig.width=5, fig.height=4}

p = cellmark(obj, group.by = "ann3", idents = c("TBX3","POMC","AGRP","KISS1"), mode = "multi",
             cols = pal$ann3, leg.pos = c(0.8,0.05), axes = F, mark.pt.size = 0.1)
p
savefig(p, filename = file.path(outdir, "plots/cellmark"),  width = 5, height = 4, format = "png")

```


# cellfeat pomc, tbx3

```{r}

p <- cellfeat(obj, features = c("POMC", "TBX3"), axes = F, merge.leg = F, theme.cols = "inferno", order = T)
p
savefig(p, filename = file.path(outdir, "plots/cellfeat_pomc_tbx3"), width = 7, height = 4, format = "png")

```

```{r fig.width=6, fig.height=8}
celldot(obj, group.by = "ann3", features = c("TBX3","PITX2","RBFOX3","GAD1", "GAD2","SLC32A1","SLC17A7","SIM1","OTX2","NEUROD1", "NEUROD6"),txtsize = 8)
```

# cell counts



```{r fig.width=4, fig.height=3}

p = cellprop(sub, x="ann3", y="group", prop = T, stack = T, cols = pal$group, x.ang = 45, txtsize = 12, x.ttl = "")
p
savefig(p, filename = file.path(outdir, "plots/fig3c"), width = 3, height = 4)

```

```{r fig.width=4, fig.height=3}
sub <- get_subset(obj, group.by = "ann3", idents=c("POMC", "TBX3", "AGRP","KISS1"))
p = cellprop(sub, x="ann3", y="bmi", cols = pal$bmi, x.ang = 45, txtsize = 12, x.ttl = "", )
p
savefig(p, filename = file.path(outdir, "plots/fig3d"), width = 4, height = 3)
```



# Highlight candidate cell types

```{r fig.width=5, fig.height=4}

clusters_to_plot <- c("TBX3", "KISS1", "AGRP", "NPY", "POMC")

for (cl in clusters_to_plot) {
  message("Plotting: ", cl)

  p <- cellmark(
    obj,
    group.by = "ann3",
    cluster.names = cl,
    mode = "multi",
    custom.colors = pal$ann3,
    legend.position = c(0.8, 0.05),
    axes = FALSE, fontsize = 14,
    highlight.size = 0.1
  )

  savefig(
    p,
    filename = file.path(outdir, paste0("plots/cellmark_", cl)),
    width = 5,
    height = 4,
    format = "png"
  )
}

```


```{r}

candidate_genes = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP")

sub = cellslice(obj, group.by = "ann3", idents = c("TBX3", "KISS1", "AGRP", "NPY", "POMC"))
sub$cellgroup <- paste(sub$ann3, sub$group, sep = "_")

p = cellmap(sub, group.by = "ann3", style = "classic", axes=F, cols=pal$ann3)
p
savefig(fig = p, filename = file.path(outdir, "plots/fig4c"),  width = 5, height = 4)

p = celldot(sub, group.by = "cellgroup", features = candidate_genes, x.ang = 45, flip = T, th.cols = "RdYlBu", rev.th.cols = T)
p
savefig(fig = p, filename = file.path(outdir, "plots/fig4d"),  width = 7, height = 5)

```




# Candidate genes expression in TBX3 cluster


```{r fig.width=6, fig.height=8}

sub = cellslice(obj, group.by = "ann3", idents = "TBX3")

p = cellvio(sub, group.by = "group", features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"), txtsize = 12,
            stack = T, pt.size = 0, ncol = 5, x.ang = 45, show.pval = T, pairwise = T, add.stats = T, cols = pal$group)
p
savefig(p, filename = file.path(outdir, "plots/cellvio_tbx3"), width = 6.5, height = 8)

```

# Candidate genes expression in POMC cluster


```{r fig.width=6, fig.height=8}

sub = cellslice(obj, group.by = "ann3", idents = "POMC")

p = cellvio(sub, group.by = "group", features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"), txtsize = 12,
            stack = T, pt.size = 0, ncol = 5, x.ang = 45, show.pval = T, pairwise = T, add.stats = T, cols = pal$group)
p
savefig(p, filename = file.path(outdir, "plots/cellvio_pomc"), width = 6.5, height = 8)

```

```{r fig.width=6, fig.height=8}

sub = cellslice(obj, group.by = "ann3", idents = "KISS1")

p = cellvio(sub, group.by = "group", features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"), txtsize = 12,
            stack = T, pt.size = 0, ncol = 5, x.ang = 45, show.pval = T, pairwise = T, add.stats = T, cols = pal$group)
p
savefig(p, filename = file.path(outdir, "plots/cellvio_kiss1"), width = 6, height = 8, format = "png")

```



```{r fig.width=6, fig.height=8}

sub = cellslice(obj, group.by = "ann3", idents = "AGRP")

p = cellvio(sub, group.by = "group", features = c("TBX3", "SIX3", "SHH", "RAX", "NKX2-1", "PRDM12", "ASCL1", 
                                "ISL1", "ASCL1", "OTP", "POMC", "KISS1","NPY", "AGRP"), txtsize = 12,
            stack = T, pt.size = 0, ncol = 5, x.ang = 45, show.pval = T, pairwise = T, add.stats = T, cols = pal$group)
p
savefig(p, filename = file.path(outdir, "plots/cellvio_agrp"), width = 6, height = 8, format = "png")

```


## Session info
```{r}
sessionInfo()
```
